### 2019-11-15 thesis.tex
FTFY

The kinetic theory is the most fundamental description of the plasma
dynamics. Based on the concepts and methods of statistical mechanics,
together with the Maxwell equations, it provides a formal self-consistent
evolution of the plasma processes. This formalism takes into account the
variations of the velocity distribution function $f({\bf r},{\bf v},t)$
in the phase-space for each particle species. Statistically, this means
that the product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species $\alpha$ in a
volume element $d^3r$ around ${\bf r}$ and in a velocity volume element
$d^3v$ around ${\bf v}$, at the instant $t$ \cite{klimon}.

>>>>

Based on the concepts and methods of statistical mechanics, together with the
Maxwell equations, the kinetic theory is the most fundamental description of
the plasma dynamics, providing a formal, self-consistent evolution of plasma
processes. As in the case of neutral gases, the kinetic formalism of plasmas
takes into account the variations of the velocity distribution function
$f({\bf r},{\bf v},t)$ in the phase-space, for each particle species.
Statistically, this means
that the product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species $\alpha$ in a
volume element $d^3r$ around ${\bf r}$ and in a velocity volume element
$d^3v$ around ${\bf v}$, at the instant $t$ \cite{klimon}.
